### 2017-12-22 master/paper.tex
Update Acknowledgment

\begin{acknowledgment}
This work was supported by JSPS KAKENHI Grant Number 15H05305.
We would like to thank Hiroaki Nagashima and Kazuaki Tanaka for supporting this research.
\end{acknowledgment}

>>>>

\begin{acknowledgment}
I would like to express my deep sense of gratitude to my adviser Professor Toshimitsu Ushio and Assistant Professor Takuya Azumi, Graduate School of Engineering Science, Osaka University, for their invaluable, constructive advice and constant encouragement during this work.
Professor Ushio and Assistant Professor Azumi's deep knowledge and their eyes for detail have inspired me much.
I am deeply grateful to my advisers Hiroshi Oyama and Hiroaki Nagashima for their helpful comments on this thesis and warm encouragement.
Finally, I would like to thank all members of Ushio Laboratory, especially the members of the Azumi team, for their kind help and cooperation.
\end{acknowledgment}
